# STAT 327 Group work on Optimization

Please write the names and email addresses of your group members.
Here's an example:

* Name / email (@wisc.edu only): John Gillett / jgillett@wisc.edu

* Name / email (@wisc.edu only): ...
* Name / email (@wisc.edu only): ...
* Name / email (@wisc.edu only): ...
* Name / email (@wisc.edu only): ...
* Name / email (@wisc.edu only): ...
* Name / email (@wisc.edu only): ...

# Part 1: One-dimensional optimization

Graph the object's altitude vs. time.

```{r}
f = function(t) {
  g = 9.81
  z0 = 100
  v0 = 55
  m = 80
  c = 15
  z=z0+(m/c)*(v0+m*g/c)*(1-exp(-c*t/m))-m*g*t/c
  z=-z
  return(z)
}

optimize(f,c(0,15))
curve(f,0,20)
abline(h=0)

```

Find the time at which the object strikes the ground.

```{r}


```

Find the object's maximum height.

```{r}
f = function(t) {
  g = 9.81
  z0 = 100
  v0 = 55
  m = 80
  c = 15
  z=z0+(m/c)*(v0+m*g/c)*(1-exp(-c*t/m))-m*g*t/c
  return(-z)
}
max_height=-optimize(f,c(0,20))$objective[1]
max_height
```

Find the time at which the object reaches its maximum height.

```{r}
f = function(t) {
  g = 9.81
  z0 = 100
  v0 = 55
  m = 80
  c = 15
  z=z0+(m/c)*(v0+m*g/c)*(1-exp(-c*t/m))-m*g*t/c
  return(-z)
}
max=optimize(f,c(0,20))
time=optimize(f,c(0,20))[1]
time
```

# Part 2: Multi-dimensional optimization

Implement `gradient.descent()`.

```{r}

```

Graph the concentration.

Use `gradient.descent()` to find the peak.

Use `optim()` with `method=Nelder-Mead` to find the peak.

Use `optim()` with `method=BFGS` to find the peak.

How many calls did `optim()` make in each case? Which method would you
expect to be faster?
