---
title: "STAT 327 Homework 3"
output:
  html_document: default
  pdf_document: default
---

We'll grade your homework by

* opening your "hw3.Rmd" file in RStudio
* clicking "Knit HTML"
* reading the HTML output
* reading your "hw3.Rmd"

You should write R code anywhere you see an empty R code chunk. You
should write English text anywhere you see "..."; please surround it
with doubled asterisks (`**...**`) so that it will show up as boldface
and be easy for us to find.

Include reasonable labels (titles, axis labels, legends, etc.) with
each of your graphs.

Name: Naiqing Cai

Email: ncai5@wisc.edu

We'll use data on housing values in suburbs of Boston. They are in an
R package called "MASS." (An R package is a collection of code,
data, and documentation. "MASS" refers to the book "Modern Applied
Statistics with S." R developed from the earlier language, S.) The
MASS package comes with the default R installation, so it's already on
your computer.  However, it's not loaded into your R session by
default. So we'll load it via the `require()` command (there's nothing
for you to do here):

```{r}
require("MASS")
```

Run `?Boston` (outside this R Markdown document) to read the help page for the `Boston` data frame.

Convert the `chas` variable to a factor with labels "off" and "on" (referring to the Charles river).

```{r}
Boston$chas = factor(Boston$chas, levels = c(0, 1), labels = c("off", "on"))
```

How many rows are in the Boston data frame? How many columns?

```{r}
b=Boston
n.rows=dim(b)[1]
cat(sep = "", "The number of rows are ", n.rows, "\n")
n.cols=length(b)
cat(sep = "", "The number of columns are ", n.cols, "\n")
```

What does a row represent?

**Each row means a unique suburb in the Boston, containing several statistics of that suburb.**


What does a column represent?

**Each column represents a different statistic that is being measured for each suburb. A column is a set of all observations of a particular statistic.**

Make a density plot (with rug) of tax rates.

```{r}
plot(density(Boston$tax),xlab='Boston$tax',main = "Tax Rates")
rug(Boston$tax)
```

Describe the shape of the distribution of tax rates.

**It is Bimodal around approximately 300 and 700.**

Note that the distribution shape doesn't make sense in light of the rug representation of the data. Make a histogram of the tax rates.

```{r}
hist(Boston$tax,breaks=100,freq=TRUE,main = "Histogram of Tax Rates",ylim = c(0, 140), xlim = c(100, 800))
```

Why is the second peak of the density plot so large? In what way is the rug representation of the data inadequate? Write a line or two of code to figure it out, and then explain it.

```{r}
max = length(which(Boston$tax == max(Boston$tax)))
cat(sep = "", "There occurs ", max, " times the maxium value ",max(Boston$tax), 
    " in this histogram.", "\n")
second = sort(Boston$tax, TRUE)[max + 1]
secondcount = length(which(Boston$tax == second))
cat(sep = "", "There occurs ", secondcount, " times the second highest value ", 
    second, " in this histogram.", "\n")
```
**Explanation:**
**At the second peak there is a very high frequency of places with a tax rate of 666 and 711, which creates such a large peak. However, on the rug, this is represented as only one dark line, which is misleading the result and that's why there would be a peak there.**

Make a barplot of "chas".

```{r}
counts = table(Boston$chas)
barplot(counts, main = "Charles River Count", xlab="label",ylim = c(0,500))
```

How many neighborhoods are on the Charles river?

```{r}
neighborhoods = length(which(Boston$chas == "on"))
cat(sep = "", "There are ", neighborhoods, " neighborhoods on the Charles river.", "\n")
```

Make a single graph consisting of three plots: 

* a scatterplot of "nox" on the y-axis vs. "dis" on the x-axis 
* a (vertical) boxplot of "nox" left of the scatterplot's y-axis
* a (horizontal) boxplot of "dis" below the scatterplot's x-axis

Hint: use `layout()` with a 4x4 matrix, using the top-right 3x3 corner
for the scatterplot, leaving the bottom-left 1x1 corner blank, and
using the other parts for the boxplots.

(An optional challenge, worth 0 extra credit points: remove the axis
and plot border from each boxplot.)

```{r, fig.width=7, fig.height=7}
layout(matrix(data=c(1, 3, 3, 3, 1, 3, 3, 3, 1, 3, 3, 3, 0, 2, 2, 2), nrow=4, ncol=4, byrow=TRUE))
boxplot(x=Boston$nox,axes=FALSE)
boxplot(x=Boston$dis,axes=FALSE,horizontal = TRUE)
plot(Boston$dis,Boston$nox)
```

Look into the highest-crime neighborhood by making a single graph of one column of three rows:

* Find the row number, r, of the neighborhood with the highest "crim".
* Make a density plot of "crim". Include a rug to show the data.
* Add a red circle at (x, y) = (max crime rate, 0) to make this maximum crime rate stand out.
* Make a density plot with rug of "medv", adding a red circle at (x, y) = (medv[r], 0) to see what medv corresponds to the highest crime rate.
* Repeat the last step for "ptratio".

```{r}
r=which(Boston$crim==max(Boston$crim), arr.ind=TRUE)
plot(density(Boston$crim),xlab='Boston$crim',main = "Crime Rates")
rug(Boston$crim)
points(max(Boston$crim),0,col='red',pch = 19)
plot(density(Boston$medv),xlab='Boston$medv',main = "Median Value of Homes")
rug(Boston$medv)
points(Boston$medv[r], 0,col='red',pch = 19)
plot(density(Boston$ptratio),xlab='Boston$ptratio',main = "Pupil Teacher Ratio")
rug(Boston$ptratio)
points(Boston$ptratio[r], 0,col='red',pch = 19)
```

What do you notice about the ptratio and medv for the highest-crime neighborhood?

**Neighborhood which Pupil Teacher Ratio is about 20, which has the highest density, has the highest-crime.**
**Neighborhood which Median Value of Homes about 10 has the highest-crime.**
